Meta-analysis of fungicide application timing experiments for powdery mildew management

### 2020-02-27 06_Publication_wireframe_and_7_Questions.Rmd
Edits and writing

---
title: Meta-analysis of fungicide application timing for powdery mildew management
  in mungbean.
author: "P. Melloy"
date: "31/01/2020"
output:
  html_document: default
---

@@

Mungbean is grown as a short season summer legume crop which can provide a high returns for growers in eastern Australia. 
A crop potentially yields up to 2.3 tonnes per hectare, with a value of up to \$ 1300 a tonne [@QueenslandGovernment2019]. 
However these potential crop yields can be limited by diseases such as powdery mildew (*Podosphaera xanthii*) by up to 40% [@Kelly2017a; @Chankaew2013]. 
Fortunately a number of strategies are able to be employed to reduce the damage powdery mildew inflicts on yields.

### Managements strategies
#### and conditions for infection
Planting date is an effective way of preventing the development of powdery mildew in mungbean. 
Powdery mildew infection requires cool temperatures (22$^\circ$ - 26$^\circ$C) and a leaf surface that is not overly wet for infection [@Kelly2017a]. 
In southern Queensland and northern New South Wales, sowing dates between late spring (November) and mid-summer (January) are advised to avoid the conducive cooler autumn temperatures which normally commence in March.  
Therefore when sowing is delayed there is a greater chance powdery mildew will infect earlier in the crop development leading to greater yield losses.

Commercially available mungbean cultivars in Australia lack sufficient resistance to be used solely as a management strategy for mitigating yield losses.
Quantitative disease resistance has been observed in breeding lines [@Pandey2018; @Chankaew2013] and mungbean cultivars such as Jade-AU, however other management strategies, such as fungicides, are still required[@Kelly2017a].

>>>>

---
title: Meta-analysis of fungicide application timing experiments for powdery mildew management
  in mungbean.
author: "P. Melloy"
date: "31/01/2020"
output:
  html_document: default
---

@@

In Australia Mungbean is grown in southern Queensland and northern New South Wales as a short season summer legume crop, with approimatley 90% of yields exported. 
Mungbean can provide a good return for growers with a potential yield of up to 2.3 tonnes per hectare, with a value of up to \$ 1300 a tonne [@QueenslandGovernment2019]. 
However these potential crop yields can be limited by diseases such as powdery mildew (*Podosphaera xanthii*) by up to 40% [@Kelly2017a; @Chankaew2013]. 
Fortunately a number of strategies are available to be employed to reduce the damage powdery mildew inflicts on yields.

### Managements strategies
#### and conditions for infection
Planting date is an effective way of preventing the development of powdery mildew in mungbean. 
Powdery mildew infection requires cool temperatures (22$^\circ$ - 26$^\circ$C) and a leaf surface that is not overly wet for infection [@Kelly2017a]. 
In southern Queensland and northern New South Wales, sowing dates between late spring (November) and mid-summer (January) are advised to avoid the conducive cooler autumn temperatures which normally commence in March.  
Therefore a delayed sowing date increases the possibility powdery mildew will infect earlier in the crop development leading to greater yield losses.

Commercially available mungbean cultivars in Australia lack sufficient resistance to be used as a sole powdery mildew management strategy.
Quantitative disease resistance has been observed in some breeding lines [@Pandey2018; @Chankaew2013]. 
In Australia there are very few availble powdery mildew resistant cultivars. 
Jade-AU is recommended as containing the best disease resistance to powdery mildew and other foliar diseases, such as tan spot and halo blight.
However other disease management strategies, such as fungicides, are still required [@Kelly2017a].
